### 2018-08-05 Sections/foreword.tex
minor
quotes

>>>>

\textit{``Any sufficiently advanced technology is indistinguishable from magic."} --- Arthur C. Clarke.
\newline \newline
\textit{``There may be babblers, wholly ignorant of mathematics, who dare to condemn my hypothesis, upon the authority of some part of the Bible twisted to suit their purpose. I value them not, and scorn their unfounded judgment."} --- Nicolaus Copernicus.
\newline \newline
\textit{``Imagination is more important than knowledge."} --- Albert Einstein.
